\documentclass[10pt]{article}
\usepackage[margin=0.8in, bottom=10mm]{geometry}
\usepackage[usenames, dvipsnames]{color}
\addtolength{\topmargin}{-0.1in}
\setlength\parindent{0pt}
\thispagestyle{empty}

\newcommand{\simsbullet}{{\raisebox{2pt}{\tiny $\bullet$}}\hspace{8pt}}
\newcommand{\midlinesimsbullet}{\hspace{4pt}{\raisebox{2pt}{\tiny $\bullet$}}\hspace{5pt}}

\begin{document}

%\sffamily

% Header. With name and address
{\centerline{\huge\bf Shane S. Sims}}
\vskip 8pt
{\centerline{\sffamily 329 West Yanonali St., Santa Barbara, CA 93101{\midlinesimsbullet}(805) 729 4411{\midlinesimsbullet}shanessims@gmail.com{\midlinesimsbullet}shanesims.me}}
% -------

\vskip 12pt

% Personal Profile or Summary or Objective
%{\Large Summary} 
%\hrule
%\vskip 6pt
%Seeking entry-level position in software engineering.
% -------

%\vskip 12pt
%\vskip 8pt

% Projects
{\Large Projects {\small - github.com/sssims}}
\vskip 1pt
\hrule
\vskip 6pt
{\bfseries\itshape\sffamily Hemingwire} \hfill \textsf{\textit{2014-2015}}\\
\textit{\textsf{hemingwire-alpha.com}} 
\vskip 4pt

\setlength{\leftskip}{16pt}

Web application built using Ruby on Rails - a social media venue for book readers to discuss novels.
\vskip 4pt
\simsbullet Developed individually over full web-application stack using Unix, Ruby, SQL, JavaScript, CSS, and HTML.\\
\simsbullet Optimized for performance. Examples include using AJAX, proper database schema and SQL joins, minimal CSS hacks, and following the ``convention over configuration'' design principle. \\
\simsbullet Leveraged as a platform to learn the Ruby on Rails framework, server configuration, and web deployment (no previous experience).

\setlength{\leftskip}{0pt}

\vskip 14pt

{\Large Professional Experience}
\vskip 2pt
\hrule
\vskip 6pt

{\bfseries\itshape\sffamily Agilysys, Inc.} \hfill \textsf{\textit{2015 - 2016}} \\
\textit{\textsf{Quality Assurance}}
\vskip 4pt

\setlength{\leftskip}{16pt}

\simsbullet Create testing schemes and assure hardware and software for release.  \\
\simsbullet Prioritize tasks using SCRUM; employ agile development methodologies. \\
\simsbullet Evaluate customer experience of products and propose improvements to development team. \\
\simsbullet Manage communications with technical contacts at partner companies to troubleshoot third party equipment and development tools. \\
\simsbullet Configure and support clients' software and hardware at customer-sites in time-constrained environments with little/poor information. 

\setlength{\leftskip}{0pt}

\vskip 8pt

{\bfseries\itshape\sffamily Advanced Industrial Modeling, Inc.} \hfill \textsf{\textit{2014 - 2015}} \\
\textit{\textsf{Software Engineer}}
\vskip 4pt

\setlength{\leftskip}{16pt}

Developed software used to optimize oil and chemical refineries.
\vskip 4pt
\simsbullet Inherited management role of certain new applets and features.  \\
\simsbullet Adapted by learning Visual Basic, VBA, and .NET framework in parallel with primary responsibilities. \\
\simsbullet Contributed over full application stack: maintained database schema, designed user experience; everything in between.  

\setlength{\leftskip}{0pt}

\vskip 8pt

{\bfseries\itshape\sffamily UC Santa Cruz -- Jack Baskin School of Engineering} \hfill {\itshape\sffamily{2011 - 2013}} \\
{\itshape\sffamily{{Tutor / Reader}}}
\vskip 4pt
\setlength{\leftskip}{16pt}
Section leader of computer science classes. Lectured in computer labs and assisted students individually; graded students' programming assignments and exams. 
\vskip 4pt
\simsbullet Prioritized time with large groups of students; identified bugs in code at a glance.\\
\simsbullet Organized crowds which would gather during sections before exams and assignment deadlines. 

\setlength{\leftskip}{0pt}


\vskip 12pt

% Educational Information
{\Large Education and Skills}
\vskip 4pt
\hrule
\vskip 6pt
{\sffamily{\bfseries University of California, Santa Cruz}}
\vskip 2pt
\hspace*{12pt} {\itshape\sffamily{B.S. Computer Science}}, {\sffamily{December 2013}} \\
\hspace*{12pt} {\itshape\sffamily{Minor Physics}}

%\vskip 16pt

% Skills
\vskip 6pt
{\sffamily{\bfseries Programming Languages} (Ordered most to least experience)}
\vskip 2pt
\hspace*{12pt} {\sffamily C, Java, C++, C\#, JavaScript, Ruby, SQL, Python, HTML, CSS, VB, VBA, LC3 Assembly}

\vskip 8pt

{\sffamily{\bfseries Technical Skills}}

\vskip 4pt

\setlength{\leftskip}{16pt}

  %\setlength{\tabcolsep}{48pt}

%\begin{center}
  \begin{tabular}{ l@{\hskip 2.2in} l }

    \simsbullet Database Systems & \simsbullet Android Applications \\
    \simsbullet Algorithm Analysis & \simsbullet Computer Architecture \\
    \simsbullet Software Design Patterns & \simsbullet Statistics \\
    \simsbullet Operating Systems & \simsbullet Data Analysis\\
    \simsbullet Test Driven Development & \simsbullet Laboratory Physics \\
    \simsbullet Object Oriented Programming & \simsbullet Quantum Mechanics \\
    \simsbullet Server Configuration & \simsbullet Calculus  \\

  \end{tabular}
%\end{center}

  %\setlength{\tabcolsep}{6pt}

\setlength{\leftskip}{0pt}
% ------

%\vskip 8pt

%\hrule

% --------

\end{document}
