\documentclass[10pt]{article}
\usepackage[margin=0.8in, bottom=10mm]{geometry}
\usepackage[usenames, dvipsnames]{color}
\addtolength{\topmargin}{-0.1in}
\setlength\parindent{0pt}
\thispagestyle{empty}
\renewcommand{\familydefault}{\sfdefault}

\newcommand{\simsbullet}{{\raisebox{2pt}{\tiny $\bullet$}}\hspace{8pt}}
\newcommand{\midlinesimsbullet}{\hspace{4pt}{\raisebox{2pt}{\tiny $\bullet$}}\hspace{5pt}}

\begin{document}

%\sffamily

% Header. With name and address
{\centerline{\huge\bf\sffamily Shane S. Sims}}
\vskip 8pt
{\centerline{\sffamily 329 West Yanonali St., Santa Barbara, CA 93101{\midlinesimsbullet}(805) 729 4411{\midlinesimsbullet}shanessims@gmail.com{\midlinesimsbullet}shanesims.me}}
% -------

\vskip 12pt

% Personal Profile or Summary or Objective
%{\Large Summary} 
%\hrule
%\vskip 6pt
{\bf\it Technology doesn't advance itself. Software engineer eager to find way to contribute programming and engineering skills to the meaningful technological advancement of humanity}
%fields include robotics, environmental technology, drones, biomedical, artificial intelligence, aerospace, and exploration.}
\vskip 18pt

{\Large\sffamily Professional Experience}
\vskip 2pt
\hrule
\vskip 6pt

{\bfseries\itshape\sffamily Advanced Industrial Modeling, Inc.} \hfill \textsf{\textit{May 2014 - April 2015; April 2016 - Present}} \\
\textit{\textsf{Software Engineer}} (C\#, .NET 5.0)
\vskip 4pt

\setlength{\leftskip}{16pt}

Full stack developer on Excel-integrated linear programming application used to optimize oil refineries. 
\vskip 4pt
\simsbullet Design application architecture, vet external API integrations; maintain unit tests. \\
\simsbullet Built custom query interface to use Microsoft Excel as pseudo-database. \\
\simsbullet User Experience design and implementation. \\
\simsbullet Adjust development priorities around changing client demands at small business with many custom solutions. 

\setlength{\leftskip}{0pt}

\vskip 16pt

{\bfseries\itshape\sffamily Agilysys, Inc.} \hfill \textsf{\textit{July 2015 - Jan. 2016}} \\
\textit{\textsf{Quality Assurance Engineer}}
\vskip 4pt

\setlength{\leftskip}{16pt}

Defined acceptance criteria for product releases; manually tested hardware and software.
\vskip 4pt
\simsbullet Validated user experience against design principles such as discoverability, useful feedback, and intuitive signifiers. \\
\simsbullet Communicated directly with users as support and during new product trials, often on-site; leveraged feedback. \\
\simsbullet Prioritized tasks using Scrum; employed agile development methodologies.

\setlength{\leftskip}{0pt}

\vskip 16pt

{\bfseries\itshape\sffamily University of California, Santa Cruz} \hfill {\itshape\sffamily{2011 - 2013}} \\
{\itshape\sffamily{{Tutor / Reader}}}
\vskip 4pt
\setlength{\leftskip}{16pt}
Section leader of computer science classes. Lectured in computer labs and assisted students individually; graded students' programming assignments and exams. 
\vskip 4pt
\simsbullet Prioritized time with large groups; adapted strategies to help students with different learning styles. \\
\simsbullet Organized crowds which would gather during sections before exams and assignment deadlines. 

\setlength{\leftskip}{0pt}

\vskip 18pt

% Projects

{\Large\sffamily Projects {\small - github.com/sssims}}
\vskip 1pt
\hrule
\vskip 6pt
{\bfseries\itshape\sffamily Hemingwire} \hfill \textsf{\textit{September 2014 - February 2015 (Abandoned)}}\\
\textit{\textsf{hemingwire-alpha.com}} 

\setlength{\leftskip}{16pt}

Twitter-esque social media web app for book readers; main goal of project was to learn new skills and languages - secondary goal was to start an entrepreneurial venture. 
\vskip 4pt
\simsbullet Full-stack development in Ruby on Rails, an MVC framework. Tools include Ruby, JavaScript, SQL, Unix.\\
%\simsbullet Evolved skillset constantly; inexperienced, new problems required research, learning, trial and error.\\
\simsbullet Adopted user-driven design philosophy. An intuitive and simple user experience was primary development priority.

\setlength{\leftskip}{0pt}

\vskip 18pt

% Educational Information
{\Large\sffamily Education and Skills}
\vskip 4pt
\hrule
\vskip 6pt
{\sffamily{\bfseries University of California, Santa Cruz}}
\vskip 2pt
\hspace*{12pt} {\itshape\sffamily{B.S. Computer Science}}, {\sffamily{December 2013}} \\
\hspace*{12pt} {\itshape\sffamily{Minor Physics}}

% Skills
\vskip 10pt
{\sffamily{\bfseries Programming Languages} (Ordered most to least experience)}
\vskip 2pt
\hspace*{12pt} {\sffamily C, C\#, JavaScript, Ruby, SQL, Java, C++, Python, HTML, CSS, VB.NET, VBA, LC3 Assembly}

\vskip 10pt

{\sffamily{\bfseries Technical Skills}}

\vskip 4pt

\setlength{\leftskip}{16pt}

  %\setlength{\tabcolsep}{48pt}

%\begin{center}
  \begin{tabular}{ l@{\hskip 2.2in} l }

    \simsbullet Algorithm Analysis & \simsbullet Computer Architecture \\
    \simsbullet Database Systems & \simsbullet Calculus \\
    \simsbullet Software Design Patterns & \simsbullet Statistics / Data Analysis\\
    \simsbullet Operating Systems & \simsbullet Quantum Mechanics \\
    \simsbullet Test Driven Development & \simsbullet Laboratory Physics \\
%    \simsbullet Object Oriented Programming & \simsbullet Quantum Mechanics \\
%    \simsbullet Server Configuration & \simsbullet Android Applications \\

  \end{tabular}
%\end{center}

  %\setlength{\tabcolsep}{6pt}

\setlength{\leftskip}{0pt}
% ------

%\vskip 8pt

%\hrule

% --------

\end{document}
